PK object batch mode trial

### 2023-06-13 data-raw/batchMode_trial_gpm.Rmd
Trying out differnt order of operations for pk object creation

```{r single_fit}
my_pk <- pk(data = my_predata) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
                                     subjects.species_harmonized))

>>>>

```{r single_fit}
my_pk <- pk(data = my_predata) +
  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
                  subjects.species_harmonized)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))
